---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>
<br>

<div align = "center"><h2>Conclusion</h2></div>
```{r summary, echo=FALSE, warning=FALSE, message=FALSE}
source("../source/Summary.R")
fat_type <- summary[[5]]
fat_2017 <- summary[[6]]
fat_2018 <- summary[[7]]
fat_2019 <- summary[[8]]
highest_death <- summary[[2]]
total_inci <- summary[[4]]
top_five_make <- summary[[3]]
porp <- summary[[1]]
```

&nbsp;&nbsp;&nbsp;&nbsp;For the first plot - the death rate of car accidents, we can find that without using any restraint is always much higher than that of using restraint. We categorized the use of restraint into three the following three types: `r fat_type`. The death rates of use of each restraint are `r fat_2017` in 2017 respectively; `r fat_2018` in 2018 respectively; and `r fat_2019` in 2019 respectively. We analyzing in the R programming. We hope to illustrate the importance of using safety restraint on the car from this data graph and highly recommend people using some protective measures on the car to protect life safety.

Depended on the second plot, it is important to know that when driving cars on the `r highest_death`, the drivers should pay more attention on these thing. Because at this place, there are many people driving their cars, that why there are so many death number. The drivers should also need to pay attention when driving on U.S. Highway, because the speed of the car on that place is super high, under this condition, it is impossible to hold it.

As for the third plot, we can find that from January 2017 to December 2019, `r total_inci` incidents occurred in USA. Among all 70 different auto makers NHTSA categorized, `r top_five_make` made up of about 25% of all incidents happened. This gives us some suggestions about buying cars.

For drugs(specified for fourth plot), the best suggestion is “Never drive when you are high with something”, even if we know there must be some people who never remember that. Something else that these data show is that people do not recognize marijuana as a kind of drug, even this factor always appears in fatal car accidents. For 2018 and 2019, marijuana has a high proportion which is around `r porp`. So when drive your cars, make sure you are not affected by drugs. This is the last suggestion we give to the readers.
